---
title: "Week 2 Peer Graded Assignment"
author: "Andy Domenico"
date: "08/27/2022"
output:
  html_document:
    df_print: paged
---

Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

This project will show a map of US Veterans Affairs locations.  Markers will contain metadata about each facility.  


```{r}
library(dplyr)
library(leaflet)
library(jsonlite)
library(readr)
```


Read the data from the json file into a data.frame
```{r}
va_data <- read_csv("data/vafacilitylocation.csv")
head(va_data)
```

rename 'longitude' to 'lng' and 'latitide' to'lat' for easier processing
```{r}
rename(va_data, lng = longitude)
rename(va_data, lat = latitude)
```

Create a leaflet map of the data, with markers for each location and a popup telling us the name of the location

```{r}
va_data %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup = va_data$name, clusterOptions=markerClusterOptions())
```













